Plot simulation results

### 2021-10-28 scripts/R/plot_simulation_results.rmd
rename file
move all figures to top-level 'figures' folder

---
title: "Plot results"
author: nadeaus
date: 31.08.21
output: html_notebook
---

@@

ggsave(plot = rmse_plot,
       filename = "manuscript/figures/simulation_RMSE.png",
       width = 4.25,
       height = 2,  # maintain height as 2 for consistent font size in manuscript
       units = "in")
```

@@

ggsave(plot = rmse_plot_with_hiv_values,
       filename = "manuscript/figures/simulation_RMSE_with_HIV_value_highlighted.png",
       width = 4.25,
       height = 2,  # maintain height as 2 for consistent font size in manuscript
       units = "in")
```

@@

ggsave(plot = tpr_plot,
       filename = "manuscript/figures/simulation_TPR.png",
       width = 5.25,
       height = 2,  # maintain height as 2 for consistent font size in manuscript
       units = "in")
```
TPR heatmap annotated with inferred POUMM values for HIV spVL
```{r}
tpr_plot_with_hiv_values <- tpr_plot +
annotate(
geom = "point",
x = 8.046, y = 3.9)  # values are hand-calculated because the breaks scale is defined as seq(0.5, n.breaks - 0.5, 1) in plotting function

>>>>

---
title: "Plot simulation results"
author: nadeaus
date: 31.08.21
output: html_notebook
---

@@

ggsave(plot = rmse_plot,
       filename = "figures/simulation_RMSE.png",
       width = 4.25,
       height = 2,  # maintain height as 2 for consistent font size in manuscript
       units = "in")
```

@@

ggsave(plot = rmse_plot_with_hiv_values,
       filename = "figures/simulation_RMSE_with_HIV_value_highlighted.png",
       width = 4.25,
       height = 2,  # maintain height as 2 for consistent font size in manuscript
       units = "in")
```

@@

ggsave(plot = tpr_plot,
       filename = "figures/simulation_TPR.png",
       width = 5.25,
       height = 2,  # maintain height as 2 for consistent font size in manuscript
       units = "in")
```
TPR heatmap annotated with inferred POUMM values for HIV spVL
```{r}
tpr_plot_with_hiv_values <- tpr_plot +
annotate(
geom = "point",
x = 8.046, y = 3.9)  # values are hand-calculated because the breaks scale is defined as seq(0.5, n.breaks - 0.5, 1) in plotting function
